Homelessness and Drug Toxicity

### 2024-03-15 paper/paper.qmd
paper updates
update model section

The goal of our modelling strategy is twofold. Firstly, use a poisson distribution and a negative binomial distribution as we have count data.Both distribution can be use on count data, and by using both we are able to compare results. Secondly, use a multilevel or Bayesian model.

@@

Define $count_i$ as the count of deaths that resulted from drug toxicity in Toronto. Then $Gender_i$ is the gender for that count of deaths and $Age group_i$ is the range of ages for the deaths.

@@

>>>>

The goal of our modelling strategy is twofold. Firstly, we use a poisson distribution and a negative binomial distribution as we have count data.Both distribution can be use on count data, and by using both we are able to compare results. Secondly, we use a multilevel or Bayesian model. We use this multilevel model to account for the nested nature of the data. All counts of deaths are nested within a year and then age group and gender. This always the model to control variance within each nested data point.

@@

Define $count_i$ as the count of deaths that resulted from drug toxicity in Toronto. Then $Gender_i$ is the gender for that count of deaths and $Age group_i$ is the range of ages for the count of deaths deaths.

@@

Thirdly, we expect changes within years as the death count increased during the pandemic seen in @age-graph. The years pre and post Covid-19 are extremely similar. There was a clear increase during the pandemic but not the topic of this paper, therefor not studied further.
